### 2019-01-07 fe_px_paper/fe_body_text.tex
Added discussion of isotope production

\textred{Comment on details of 51/52Mn production here...}

Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
% , which makes activity quantification trivial.
% In addition, 
\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.

\textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}

In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
These include the non-standard positron emitters 
\ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
\ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
\ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x). 
The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.

>>>>

\textred{All: feel free to add additional details of 51/52Mn production here...}

Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reaction below 70\,MeV to date, with cross sections measured  at the 4--9\% uncertainty level.
This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date. 
\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr \cite{Klein2000}.
However, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} could be used for clean production of  \ce{^{51}Mn} ($\geq$98.8\% radioisotopic purity) below 20\,MeV using the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} channel.
In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house of this short-lived ($t_{1/2}=46.2\pm0.1$ m \cite{Wang2017}) radionuclide.
To increase yields, an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons.

Likewise, \ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%) \cite{Graves2015,Wooten2015}.
\ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the low radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn}, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d \cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,m \cite{Dong2015}) can be easily separated through the difference in lifetime, to avoid the unfavorable gammas produced by the isomer. 
However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$\pm$0.008\,h \cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator.
Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.

% step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
% \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
% , which makes activity quantification trivial.
% In addition, 
% \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
% Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
% Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
% This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.

% \textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}

In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
These include the non-standard positron emitters 
\ce{^{44}Sc} \cite{Muller2013,Filosofov2010,Qaim2011}
% \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
\ce{^{55}Co} \cite{Thisgaard2011,Zaman1996,Hermanne2000a}
\ce{^{61}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
\ce{^{61}Cu} \cite{Szelecsenyi2005a,Fukumura2004}
\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
% \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
% \ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
% \ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
and the $\beta^-$-therapeutic agent 
\ce{^{47}Sc} \cite{Muller2014,Deilami-nezhad2016}.
% and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x). 
% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
